 \begin{thebibliography}{9}
        
        \bibitem{sus_bat_1}		
		\textit{Batteryuniversity.com. 2021. How to Recycle Batteries - Battery University. Available: https://batteryuniversity.com/learn/article/recycling\_batteries}
		\bibitem{sus_bat_2}		
		\textit{Candor Industries. 2021. PCB Recycling: How to Recycle Circuit Boards - Candor. Available: https://www.candorind.com/pcb-recycling/\#thermal-recovering}
		\bibitem{sus_hou_1}
        \textit{F. d. B. Ana Morao, “Life cycle impact assessment of polylactic acid (pla) produced from sugarcane in thailand.” Journal of Polymers and the Environment, 2019, pp. 2523–2539. Available: https://doi.org/10.1007/s10924-019-01525-9}
        \bibitem{sus_hou_2}
        \textit{ J. J. Shen, “Comparative life cycle assessment of polylactic acid (pla) and polyethylene terephthalate (pet),” 2011.}
        \bibitem{sus_dis}
        \textit{T. R. Walker, O. Adebambo, M. C. Del Aguila Feijoo, E. Elhaimer, T. Hossain, S. J. Edwards, C. E. Morrison, J. Romo, N. Sharma, S. Taylor, and S. Zomorodi, “Chapter 27 - environmental effects of marine transportation,” in World Seas: an Environmental
Evaluation (Second Edition), second edition ed., C. Sheppard, Ed. Academic Press, 2019, pp.
505–530.Available: https://www.sciencedirect.com/science/article/pii/B9780128050521000309}
		\bibitem{sus_usg}
        \textit{Lithium-Ion Battery Maintenance Guidelines, Tektronix, inc, 2021. Available: https://www.newark.com/pdfs/techarticles/tektronix/LIBMG.pdf }
        \bibitem{sus_eol_1}
        \textit{Batteryuniversity.com. 2021. How to Recycle Batteries - Battery University. Available at: https://batteryuniversity.com/learn/article/recycling\_batteries } 
        \bibitem{sus_eol_2}
        \textit{Candor Industries. 2021. PCB Recycling: How to Recycle Circuit Boards - Candor. Available at: https://www.candorind.com/pcb-recycling/\#thermal-recovering}
				
		


		


		

    \end{thebibliography}