\subsection*{Environmental impact of the Limpet}


\subsubsection*{Battery}
The batteries are taken off the limpet at the end of life and ship to the battery recycling place. The battery replaces remove all the non-metal part and ship the mixed metal to metal separation factory \cite{sus_bat_1}. PCB of the limpet can be recycled in three ways at the end of life, thermal recovering, chemical recovering, and physical recovering \cite{sus_bat_2}. \\

For the thermal recovering process, you must heat the PCB to a high temperature to recover the metals present on the board. FR-4 is a composite material composed of woven fiberglass cloth with an epoxy resin binder that is flame resistant (self-extinguishing). Thermal recovery will incinerate the FR-4 but retain the copper. This method will create harmful gases in the air like lead and dioxin. 
For the chemical recovering process, a bed of acid to recover the metal from the PCB. The board gets put into the acid, which destroys the FR-4 again, and it also creates a large quantity of wastewater that needs treatment before disposing it. \\

The physical recovering process involves the shredding, smashing, breaking, and separating of the metal from non-metal components. While this method does have the least environmental impact.
It is a hazard for everyone working around the PCB because you are sending dust, metal, and glass particles into the air, which can lead to respiratory issues if exposed for prolonged periods. This method does retain all the metal components.



\subsubsection*{Housing}
The housing for this project is constructed using a 3D printer with PLA. PLA is made from
fermented plant starch such as corn or sugar cane. The growth of these plants requires land
preparation, maintenance and harvesting. The impacts of growing fermented planets on the
environment is through power usage or chemicals. For sugarcane grown PLA, the total CO2
emissions from growth to production is 501kg/ton PLA \cite{sus_hou_1}. PLA plastic emits less CO2 than
other types of 3D printer materials at the transportation stage \cite{sus_hou_2}.

\subsubsection*{Distribution}
The developed devices could be sold individually or attached to desk shipped via freight
ships. The environmental impact would then be dependent on the number of devices
shipped together. Freight ships have a wide range of ecological effects, including air
pollution, spillage, ship-strikes on marine megafauna and ballast water containing aquatic
invasive species \cite{sus_dis}.
Individually sold devices would need to be manually installed by the customer. Shipping
these would be best done in bulk to the office. The practical impact per device can be kept
down if the devices are sent together. Shipping many devices to a distributor would be the
best option. From the distributor, the devices could be placed onto a desk and reshipped.

\subsubsection*{Usage}
The Limpets are going to be used in offices. It has both operational requirements and
maintenance requirement for usability.
A primary operational requirement for the Limpet is energy. Energy for the Limpet comes in
the form of a Lithium button battery. Ten years is the operational lifespan of a Lithium
button battery \cite{sus_usg}. Using a battery instead of an external energy source means that the
Limpet has no effect on energy consumption during operation. Due to the batteries require
replacement instead of charging. Limpets’ features mean that energy use improvements can
be implemented, reducing overall energy use even with increased use of the Limpets.
In the case of a Limpet requiring repairs, the device would be replaced. Replacement
instead of repairing is due to the Limpets being a low-cost device, and incurred costs of
repairing a Limpet may be more than the Limpet’s worth.

\subsubsection*{End of life}
The batteries are taken off the Limpet at the end of life and ship to the battery recycling
place. The battery recycling place removes all the non-metal parts and ships the mixed
metal to the metal separation factory \cite{sus_eol_1}. The housing of the Limpet is collected and
recycled at a PLA recycle factory. PCB of the Limpet can be recycled in three ways at the end
of life, thermal recovering, chemical recovering, and physical recovering \cite{sus_eol_2}.
For the thermal recovering process, PCB must be heated to a high temperature to recover
the metals present on the board. FR-4 is a composite material composed of woven fibreglass
cloth with an epoxy resin binder that is flame resistant. Thermal recovery will incinerate the
FR-4 but retain the copper. This process creates harmful gases in the air like lead and dioxin.
For the chemical recovering process, a bed of acid to recover the metal from the PCB. The
PCB board is put into the acid, destroys the FR-4. This process creates a large quantity of
wastewater that needs treatment before disposing of into the ocean.
The physical recovering process involves shredding, smashing, breaking, and separating the
metal from non-metal components. This method has the most negligible environmental
impact. It is a hazard for everyone working around the PCB. This process sends dust, metal,
and glass particles into the air, leading to respiratory issues if exposed for prolonged periods.
This method does retain all the metal components from the PCB.

\subsection*{Social impact of the Limpet }
The Limpet system allows companies to builds the more comfortable and more efficient working environment for their employees. Employees who works within this working environment will have less stress, therefore, less mental diseases.\\

The effect of the Limpet is not only limited to the office space but also in other parts of the society. Happier employees become happier parents, happier flatmates, and many other happier roles in the society, which has a significant impact on social environments. There will be less fighting and arguing around which leads to a more positive and peaceful society. 

\subsection*{Energy impacts of the Limpets }
Office electronics can be controlled by the hot-desking of the Limpets. If nobody is in an office area, lights can be turned off; Air conditioning can be turned off; Fan can be turned off. With the 3D distance mesh system, some office structure analysis can analyze the position of the air-condition placement. Air conditioning can be placed in the places of most usage to save energy. This can minimize the cost of using the air conditioning. All features stated above achieved the purpose of energy saving.
